Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-02-20 writeup/gz_hubble_data.tex
New figure and code for filter curves

We use different filters for the north and south GOODS fields so that GEMS can be directly compared with GOODS-S.

@@

This project made heavy use of the Astropy packages in Python \citep{ast13}, as well as the \texttt{seaborn} plotting package \citep{was15}.

>>>>

We use different filters for the north and south GOODS fields so that GEMS can be directly compared with GOODS-S (Figure~\ref{fig:filtercurves}).

\begin{figure*}
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \textit{HST} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in Galaxy Zoo: Hubble. The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope which were used to create color gradients in the composite images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

@@

This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, and astroML \citep{van12}.
